Notes on 10d Super Yang-Mills

### 2019-03-24 10d_SYM_Notes.tex
SUSY invariance of 10d SYM

\newcommand{\map}{\ul{\mr{Map}}}
\newcommand{\dBRST}{\mathrm d_{\mathrm{BRST}}}
\renewcommand{\d}{\mathrm{d}}
\newcommand{\sD}{\slashed{D}}
\newcommand{\sdel}{\slashed{\partial}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\sdelbar}{\overline{\slashed{\partial}}}
\newcommand{\st}[1]{{}^*{#1}}

@@

The action functional in 10d super Yang-Mills is given by
\[S(A,\lambda) = \int_{\RR^{10}} \langle F_A \wedge \ast F_A + (\lambda, \sd D_A \lambda)\rangle,\]
where $\langle - \rangle$ denotes an invariant pairing on $\gg$, and $(,)$ denotes a scalar-valued pairing $S_+ \otimes S_- \to \CC$ (there will be a unique such pairing, up to rescaling, characterized by the condition that $(\rho(v)\lambda_1,\rho(v)\lambda_2) = (\lambda_1,\lambda_2)$ for each $v \in \CC^{10}$, where $\rho$ denotes Clifford multiplication).

@@

%Failure to commute with the classical BV differential

>>>>

\newcommand{\C}{\mathbf{C}}
\newcommand{\dBRST}{\mathrm d_{\mathrm{BRST}}}
\renewcommand{\d}{\mathrm{d}}
\newcommand{\sD}{\slashed{D}}
\newcommand{\sdel}{\slashed{\partial}}
\newcommand{\map}{\ul{\mr{Map}}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\sdelbar}{\overline{\slashed{\partial}}}
\newcommand{\st}[1]{{}^*{#1}}

@@

The action functional in 10d super Yang-Mills is given by
\[S(A,\lambda) = \int_{\RR^{10}} \langle \frac{1}{2} F_A \wedge \ast F_A - (\lambda, \sd D_A \lambda)\rangle,\]
where $\langle - \rangle$ denotes an invariant pairing on $\gg$, and $(,)$ denotes a scalar-valued pairing $S_+ \otimes S_- \to \CC$ (there will be a unique such pairing, up to rescaling, characterized by the condition that $(\rho(v)\lambda_1,\rho(v)\lambda_2) = (\lambda_1,\lambda_2)$ for each $v \in \CC^{10}$, where $\rho$ denotes Clifford multiplication).

@@

\subsection{$SU(5)$-invariant splitting}

We will need an expression for the Hodge star operator on K\"{a}hler manifolds, see \cite[Proposition 1.2.31]{Huybrechts}.

\begin{prop}
Let $M$ be a K\"{a}hler $d$-fold and decompose
\[\Omega^2(M; \C) = \Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)\oplus (\C\omega\oplus \Omega^{1, 1}_\perp(M)).\]
Then
\begin{enumerate}
\item The spaces $\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$, $\C\omega$ and $\Omega^{1, 1}_\perp(M)$ are mutually orthogonal.

\item For $\alpha\in\Omega^{2, 0}(M)\oplus \Omega^{0, 2}(M)$ we have
\[\ast \alpha = \frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]

\item For $\alpha\in \Omega^{1, 1}_\perp(M)$ we have
\[\ast\alpha = -\frac{1}{(d-2)!} \alpha\wedge \omega^{d-2}.\]

\item For $\alpha\in\C\omega$ we have
\[\ast \alpha = \frac{1}{(d-1)!} \alpha\wedge \omega^{d-2}.\]
\end{enumerate}
\end{prop}

\begin{corollary}
Let $M$ be a K\"{a}hler $d$-fold. Then
\[F\wedge \ast F + \frac{1}{(d-2)!} F\wedge F\wedge \omega^{d-2} = \left(4(F_{2, 0}, F_{0, 2}) + (\Lambda F_{1, 1})^2\right) \frac{\omega^d}{d!}.\]
\end{corollary}

Pick a reduction of the structure group to $SU(5)\subset SO(10)$. This gives rise to a K\"{a}hler structure $\omega$ on $\R^{10}$ and a nonvanishing holomorphic 5-form $\Omega$. We denote by $\Lambda\colon \Omega^k(M)\rightarrow \Omega^{k-2}(M)$ the dual Lefschetz operator defined by $(\Lambda \alpha, \beta) = (\alpha, \beta\wedge \omega)$.

The connection splits as $A = A_{0, 1} + A_{1, 0}$. The semi-spin representation decomposes as
\[S_+ \cong \C\oplus \Omega^{0, 2} \oplus \Omega^{1, 0},\]
which gives rise to a decomposition $\lambda = \chi + B + \psi$.

If $Q\in S_+$ is the scalar supercharge, the supersymmetry transformations become
\begin{align*}
\delta_Q A_{1, 0} &= \psi \\
\delta_Q B &= F_{0, 2} \\
\delta_Q \chi &= \frac{1}{2} \Lambda F_{1, 1}.
\end{align*}
Note that $\delta_Q^2 \chi = \frac{1}{2} \Lambda(\overline{\partial} \psi)$ and zero on other fields.

Let
\[S_{top} = \frac{1}{12}\int F\wedge F\wedge \omega^3\]
be the instanton number. Then we get
\[
S + S_{top} = \int \frac{\omega^5}{5!}\left(2(F_{2, 0}, F_{0, 2}) + \frac{1}{2} (\Lambda F_{1, 1})^2 - 2\Lambda(\overline{\partial}\psi) \chi - 2(B, \partial \psi)\right) - B\wedge \overline{\partial} B\wedge \Omega
\]

We then have
\[\delta_Q(S+S_{top}) = \int \frac{\omega^5}{5!}\left(2(F_{0, 2}, \partial \psi) + \Lambda F_{1, 1} \Lambda(\overline{\partial}\psi) - \Lambda F_{1, 1} \Lambda(\overline{\partial}\psi) - 2(F_{0, 2}, \partial \psi)\right) = 0.
\]

Note that $\delta_Q S_{top} = 0$ (it is a topological invariant). Therefore, $\delta_Q S = 0$. We have checked it for a pure spinor supercharge. The span of pure spinors in $S_+$ is an $SO(10)$-subrepresentation which by irreducibility has to be everything. Thus, any spinor is a linear combination of pure spinors and so $\delta_Q S = 0$ for any supercharge $Q$.
